---
name: "José Daniel Conejeros, MSc, BSc"
#date: 'UP: Enero 2023'
position: "[MSc in Sociology](http://sociologia.uc.cl/postgrado/magister-en-sociologia/) & [Statistics](https://www.mat.uc.cl/me.html) | Pontificia Universidad Católica de Chile"
#profilepic: JConejeros.jpg
email: jdconejeros@uc.cl
www: jd-conejeros.com
github: github.com/JDConejeros
orcid: orcid.org/0000-0003-3402-4361
twitter: jose_conejeros
linkedin: joseconejerosp
researchgate: Jose-Conejeros
phone: +56 9 6492 4057
aboutme: "**Areas of Interest:** Social vulnerabilities, infectious diseases, physical and mental health and statistical modeling techniques."
headcolor: "203C60"
csl: apa-cv.csl # change this if you want to use other citation styles
output: 
  vitae::awesomecv:
    pandoc_args: ["--lua-filter=lua/bib_bold.lua"] 
    keep_tex: true
header-includes:
- \geometry{left=2cm, top=2cm, right=2cm, bottom=2cm, footskip=0.5cm}
- \newcommand{\bcenter}{\begin{center}}
- \newcommand{\ecenter}{\end{center}}
- \fancyfoot[L]{\fontsize{8pt}{-1em}\footerfont\color{lighttext}{Page \thepage \ of \pageref{LastPage}}}
- \fancyfoot[R]{\fontsize{8pt}{-1em}\footerfont\color{lighttext}{Revised February 2023}}
---


```{r setup, include=FALSE}
library(tidyverse)
library(vitae)
library(here)
library(glue)
library(tibble)

knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  cache = FALSE
)
```

```{r get data, include=FALSE}
## Education
edu <- read_csv2(here::here("data", "ENG", "education.csv"))
#edu2 <- read_csv2(here::here("data", "ENG", "education2.csv"))

## Research Experience 
jobs1 <- read_csv2(here::here("data", "ENG", "jobs1.csv"))

## Research center
centers <- read_csv2(here::here("data", "ENG", "centers.csv"))

## Consulting Experience 
jobs2 <- read_csv2(here::here("data", "ENG", "jobs2.csv"))

## Training
training <- read_csv2(here::here("data", "ENG", "training.csv"))

## Teaching 
teaching1 <- read_csv2(here::here("data", "ENG", "teaching1.csv"))
teaching2 <- read_csv2(here::here("data", "ENG", "teaching2.csv"))

## Volunter
services1 <- read_csv2(here::here("data", "ENG", "services1.csv"))
services2 <- read_csv2(here::here("data", "ENG", "services2.csv"))

## Skils
skills <- read_csv2(here::here("data", "ENG", "skills.csv")) %>% 
  group_by(category) %>% 
  mutate(skill = paste(skill, collapse = " - ")) %>% 
  ungroup %>% 
  unique

## Grants
grants <- read_csv2(here::here("data", "ENG", "grants.csv"))

## Presentations
presentations <- read_csv2(here::here("data", "ENG", "presentations.csv"))

## References
reference <- read_csv2(here::here("data", "ENG", "reference.csv"))
```


# Education

```{r}
detailed_entries(edu, 
                 when = glue("{start_date}--{end_date}"),
                 what = degree,
                 #where = loc,
                 #with = uni
                 why = details
                 )
```

# Profesional Employment

```{r}
jobs1 %>% 
  detailed_entries(
    what = role,
    when = glue("{start_date}--{end_date}"),
    #with = company,
    #where = where,
    why = details)
```


\fontsize{9pt}{1em}\bodyfontlight\upshape\color{text}

*A Fondecyt Regular is a scientific research project funded by the National Agency for Research and Development ([ANID](https://www.anid.cl/proyectos-de-investigacion/fondecyt-regular/), Chile).


# Publications

\fontsize{10pt}{1em}\bodyfontlight\upshape\color{text}

## Journal articles

```{r}
bibliography_entries("data/my_papers.bib")
```

## Work in progress

```{r}
bibliography_entries("data/my_wip.bib")
```

\break

## Book chapters

```{r}
bibliography_entries("data/my_bookch.bib")
```

\fontsize{10pt}{1.5em}\bodyfontlight\upshape\color{text}

# Conferences, Workshops, and Talks

```{r}
presentations %>% 
  detailed_entries(
    what = what,
    with = with,
    when = when,
    where = where,
    why = why)
```

# Teaching

## Undergraduate

```{r}
teaching1 %>% 
  detailed_entries(
    what = role,
    when = glue("{start_date}--{end_date}"),
    #with = company,
    #where = where,
    why = details)
```

## Postgraduate

```{r}
teaching2 %>% 
  detailed_entries(
    what = role,
    when = glue("{start_date}--{end_date}"),
    #with = company,
    #where = where,
    why = details)
```


# Professional Memberships

```{r}
centers %>% 
  detailed_entries(
    what = what,
    #with = with,
    when = when,
    #where = where,
    why = why)
```

# Profesional Service

```{r}
jobs2 %>% 
  detailed_entries(
    what = role,
    when = glue("{end_date}"),
    #with = company,
    #where = where,
    why = details)
```


# Certificates and Training

```{r}
training %>% 
  detailed_entries(
    what = what, 
    #with = with, 
    when = when, 
    #where = where, 
    why = why)
```


# Special Skills

```{r}
skills %>% 
  detailed_entries(
    why = skill, 
    what = category)
```


# Scholarships and awards

```{r}
grants %>% 
  detailed_entries(
    why = why, 
    what = with, 
    when = when)
```

# Service

## Social Participation

```{r}
services1 %>% 
  detailed_entries(
    what = role,
    when = glue("{start_date}--{end_date}"),
    #with = company,
    #where = where,
    why = details)
```


## Teaching Assistants (student)

```{r}
services2 %>% 
  detailed_entries(
    what = role,
    when = glue("{start_date}--{end_date}"),
    #with = company,
    #where = where,
    why = details)
```
# References 

```{r}
reference %>% 
  detailed_entries(
    what = what, 
    when = when,
    with = with, 
    where = where, 
    why = why)
```


\vspace*{\fill}

\begin{footnotesize}
\bcenter
This document was prepared in \href{https://rmarkdown.rstudio.com/}{R-markdown} with the `vitae` library. 

To replicate you can use the source code here: \href{https://github.com/JDConejeros/CV}{https://github.com/JDConejeros/CV}
\ecenter
\end{footnotesize}

<!--Repositorio de vitae: https://github.com/mitchelloharawild/vitae -->

